\Title

### 2020-03-04 manuscript/manuscript.tex
Change ranges on airborne nb and update parameters table
Change parameters on gridding airborne survey notebook to ranges when
possible. Update parameters table on manuscript.

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{l c c c}
        & \textbf{Sources bellow data} & \textbf{Block median sources}
        & \textbf{Grid sources} \\

        \textbf{Constant depth} & & & \\
        \hline
        Depth (km) & \AirborneSourceBellowDataConstantDepthDepth
                   & \AirborneBlockMedianSourcesConstantDepthDepth
                   & \AirborneGridSourcesConstantDepthDepth \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesConstantDepthSpacing
                     & \AirborneGridSourcesConstantDepthSpacing \\
        Pad & -
            & -
            & \AirborneGridSourcesConstantDepthPad \\

        & & & \\
        \textbf{Relative depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBellowDataRelativeDepthDepth
                   & \AirborneBlockMedianSourcesRelativeDepthDepth
                   & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesRelativeDepthSpacing
                     & \\

        & & & \\
        \textbf{Variable depth} & & & \\
        \cline{1-3}
        Depth (km) & \AirborneSourceBellowDataVariableDepthDepth
                   & \AirborneBlockMedianSourcesVariableDepthDepth
                   & \\
        Depth factor & \AirborneSourceBellowDataVariableDepthDepthFactor
                     & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                     & \\
        K nearest & \AirborneSourceBellowDataVariableDepthKNearest
                  & \AirborneBlockMedianSourcesVariableDepthKNearest
                  & \\
        Spacing (km) & -
                     & \AirborneBlockMedianSourcesVariableDepthSpacing
                     & \\
    \end{tabular}
\end{table*}

>>>>

\begin{table*}
    \centering
    \caption{
        Parameters used with each source distribution when gridding the
        synthetic airborne survey.
    }
    \label{tab:parameters-airborne-survey}
    \begin{tabular}{c | l l c c}
        \multicolumn{1}{c}{\textbf{Source layout}}
            & \multicolumn{1}{c}{\textbf{Depth type}}
            & \multicolumn{1}{c}{\textbf{Parameters}}
            & \multicolumn{1}{c}{\textbf{Values}}
            & \multicolumn{1}{c}{\textbf{Interval}} \\
        \hline

        \multirow{8}{*}{Source Bellow Data}
            & \multirow{2}{*}{Constant Depth}
                & Depth (km)
                & \AirborneSourceBellowDataConstantDepthDepth
                & \AirborneSourceBellowDataConstantDepthDepthInterval \\
            &
                & Damping
                & \AirborneSourceBellowDataConstantDepthDamping
                & \AirborneSourceBellowDataConstantDepthDampingInterval \\
            \cline{2-5}
            & \multirow{2}{*}{Relative Depth}
                & Depth (km)
                & \AirborneSourceBellowDataRelativeDepthDepth
                & \AirborneSourceBellowDataRelativeDepthDepthInterval \\
            &
                & Damping
                & \AirborneSourceBellowDataRelativeDepthDamping
                & \AirborneSourceBellowDataRelativeDepthDampingInterval \\
            \cline{2-5}
            & \multirow{4}{*}{Variable Depth}
                & Depth (km)
                & \AirborneSourceBellowDataVariableDepthDepth
                & \AirborneSourceBellowDataVariableDepthDepthInterval \\
            &
                & Depth factor
                & \AirborneSourceBellowDataVariableDepthDepthFactor
                & \AirborneSourceBellowDataVariableDepthDepthFactorInterval \\
            &
                & K nearest
                & \AirborneSourceBellowDataVariableDepthKNearest
                & \AirborneSourceBellowDataVariableDepthKNearestInterval \\
            &
                & Damping
                & \AirborneSourceBellowDataVariableDepthDamping
                & \AirborneSourceBellowDataVariableDepthDampingInterval \\
        \hline

        \multirow{11}{*}{Block median sources}
            & \multirow{3}{*}{Constant Depth}
                & Depth (km)
                & \AirborneBlockMedianSourcesConstantDepthDepth
                & \AirborneBlockMedianSourcesConstantDepthDepthInterval \\
            &
                & Spacing (km)
                & \AirborneBlockMedianSourcesConstantDepthSpacing
                & \AirborneBlockMedianSourcesConstantDepthSpacingInterval \\
            &
                & Damping
                & \AirborneBlockMedianSourcesConstantDepthDamping
                & \AirborneBlockMedianSourcesConstantDepthDampingInterval \\
            \cline{2-5}
            & \multirow{3}{*}{Relative Depth}
                & Depth (km)
                & \AirborneBlockMedianSourcesRelativeDepthDepth
                & \AirborneBlockMedianSourcesRelativeDepthDepthInterval \\
            &
                & Spacing (km)
                & \AirborneBlockMedianSourcesRelativeDepthSpacing
                & \AirborneBlockMedianSourcesRelativeDepthSpacingInterval \\
            &
                & Damping
                & \AirborneBlockMedianSourcesRelativeDepthDamping
                & \AirborneBlockMedianSourcesRelativeDepthDampingInterval \\
            \cline{2-5}
            & \multirow{5}{*}{Variable Depth}
                & Depth (km)
                & \AirborneBlockMedianSourcesVariableDepthDepth
                & \AirborneBlockMedianSourcesVariableDepthDepthInterval \\
            &
                & Depth factor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactor
                & \AirborneBlockMedianSourcesVariableDepthDepthFactorInterval \\
            &
                & K nearest
                & \AirborneBlockMedianSourcesVariableDepthKNearest
                & \AirborneBlockMedianSourcesVariableDepthKNearestInterval \\
            &
                & Spacing (km)
                & \AirborneBlockMedianSourcesVariableDepthSpacing
                & \AirborneBlockMedianSourcesVariableDepthSpacingInterval \\
            &
                & Damping
                & \AirborneBlockMedianSourcesVariableDepthDamping
                & \AirborneBlockMedianSourcesVariableDepthDampingInterval \\
        \hline

        \multirow{4}{*}{Grid Sources}
            & \multirow{4}{*}{Constant Depth}
                & Depth (km)
                    & \AirborneGridSourcesConstantDepthDepth
                    & \AirborneGridSourcesConstantDepthDepthInterval \\
            &
                & Spacing (km)
                    & \AirborneGridSourcesConstantDepthSpacing
                    & \AirborneGridSourcesConstantDepthSpacingInterval \\
            &
                & Pad
                    & \AirborneGridSourcesConstantDepthPad
                    & \AirborneGridSourcesConstantDepthPadInterval \\
            &
                & Damping
                    & \AirborneGridSourcesConstantDepthDamping
                    & \AirborneGridSourcesConstantDepthDampingInterval \\
    \end{tabular}
\end{table*}
